---
title: "Mathematics for Economics Class Notes"
author: "Farbod Alinezhad"
output: html_notebook
---
```{r, setup, include = F}
library(matlib)
```
# Introduction
I am taking this course as a part of my PhD. The full name of the course is Mathematics for Economists. It goes through linear algebra, calculus, and statistics related to economics. It uses R programming language for most of its exercises.


## Modules 1 and 2
These modules were about linear algebra. The topics included an introduction to matrices and their uses in economics, solving equations, matrix inverses, determinants, etc.

### Assignment
\
Variables from the assignment:
```{r}
k<-10

A<-matrix(c(1,2,3,2,1,4,3,4,1), 3,3, byrow=TRUE)

B<-matrix(c(7,8,9,8,7,10,19,12,13), 3,3, byrow=TRUE)

W<-matrix(c(2,5,3,5,5,7), 3,2, byrow=TRUE)

D<-c(10, 22, 14)

E<-c(13, 17)

Repeat<-c(5,5,7)

Zero<-c(0,0,0)

Unit<-c(1,1,1)

```
**Questions**

1. what is KD? `r k*D`
2.	What is UnitD? `r Unit %*% D`
3.	What is DDT?
```{r, echo = F}
D %*% t(D)
```
4.	What is DTD?
```{r, echo = F}
t(D) %*% D
```
5.	What is A+B? `r A + B`
6.	What is A-B?
7.	What is DA?
8.	What is AD?
9.	What is BD?
10.	What is DB?
11.	What is AB?
12.	What is BA
13.	What is ATBT?
14.	What is BTAT
15.	What is (AB)T
16.	What is A-1?
```{r, echo = F}
inv(A)
```
17.	What is B-1?
18.	What is A-1B-1?
19.	What is B-1A-1?
20.	What is (AB)-1?
21.	What is (BA)-1?
22.	What is D concatenated with E (E follows D)?
23.	What is AW?
24.	What is WA?
25.	What is WTW?
26.	What is WWT?
27.	What is det(A)?
28.	What is AA-1?
29.	What is A-1A?
30.	How does the structure of A differ from that of B? (Think in matrix terms.)
31.	What is W-1?
32.	Put A in row reduced echelon form (RREF)
33.	Put W in RREF
